### 2018-01-26 ApproxComp/sec-conclusion.tex

In this article we have systematiclly introduced approximation computation techniques toward efficient and effective big data analytics.
Furthermore, although approximate computation does not put
theoretical bounds with respect to optimal solutions, it does expect a balance between efficiency and accuracy. Indeed, (1) our query approximation techniques~\cite{tods-MaCFHW14,LinMZWH17,MaHWLH17} show that efficiency can be obtained with high accuracy in practice, and (2) our data approximation techniques for shortest paths and distances and link prediction~\cite{MaFLWCH16,DuanMAMH17} show that efficiency and accuracy can be obtained for certain data analytic tasks. That is, the design policy approximate computation of is not to sacrifice effectiveness for efficiency, but to achieve both efficiency and effectiveness in practice.

>>>>

In this article we have systematiclly introduced approximation computation techniques toward efficient and effective big data analytics.
Furthermore, although approximate computation does not put
theoretical bounds with respect to optimal solutions, it does expect a balance between efficiency and quality. Indeed, (a) our query approximation techniques~\cite{tods-MaCFHW14,LinMZWH17,MaHWLH17} show that efficiency can be obtained with high accuracy in practice, and (b) our data approximation techniques for shortest paths and distances and link prediction~\cite{MaFLWCH16,DuanMAMH17} show that efficiency and accuracy can be obtained simultaneously for certain data analytic tasks. That is, the design policy approximate computation is not to sacrifice effectiveness for efficiency, but to achieve both efficiency and effectiveness in practice.

### 2018-01-26 ApproxComp/sec-data.tex

Big data has large volume, and, hence, the space complexity of big data analytic tasks starts raising more concerns.
Given a class $Q$ of queries on a data set $D$, data approximation is to transform $D$ into a smaller data set $D'$ such that $Q$ on $D'$ returns a satisfiable approximate answer in a more efficient way. Further, it is typically common that query $Q$ needs to be (slightly) modified to $Q'$ to accommodate  the changes of $D$ to $D'$, as shown in Fig.~\ref{fig-tech-dataappro}. Similar to query approximation, data approximation needs to reach a balance between the query efficiency and answer accuracy.

The rationale of data approximation has roots in the Pareto principle\footnote{\small \url{https://en.wikipedia.org/wiki/Pareto_principle}} that ``states that, for many events, roughly 80\% of the effects come from 20\% of the causes''. The critical thing for data approximation is to determine which part of data is relevant to tasks (belong to the 20\%).
 By this principle, for many big analytic tasks, one may only need to keep a small amount of the data to derive ``satisfiable'' answers.
For example, when we are to build a predictive model on the stock of razers for an online store based on the order history of customers, orders from men are good enough. While on the stock of lipsticks, those from women are good enough. That is to say,  it is not necessary to use the entire data for certain data analytic tasks.

However, it should be pointed out that there are data analytic tasks such that data approximation could not work well. For example, an online store needs to count the total number of goods in its catalog.  Essentially the entire goods should be considered for this task, and if a (small) portion of goods are chosen, it is hard to have a ``satisfiable'' result.

We next explain data approximation computation in more detail with three different data analytic tasks.

@@

\begin{figure}[tb!]
  \vspace{-1ex}
  \begin{center}
  \includegraphics[scale=0.45]{./dataApprox.png}
  \end{center}
  \vspace{-3ex}
  \caption{Data approximation}\label{fig-tech-dataappro}
  \vspace{-2ex}
\end{figure}

>>>>

Big data has large volume, and, hence, the space complexity~\cite{CormenLRS01} of big data analytic tasks starts raising more concerns.
Given a class $Q$ of queries on data $D$, data approximation is to transform $D$ into smaller $D'$ such that $Q$ on $D'$ returns a sufficient or satisfiable approximate answer in a more efficient way. Further, it is typically common that query $Q$ needs to be (slightly) modified to $Q'$ to accommodate  the changes of $D$ to $D'$, as shown in Fig.~\ref{fig-tech-dataappro}. Similar to query approximation, data approximation needs to reach a balance between the query efficiency and answer quality.

The rationale behind data approximation has roots in the Pareto principle\footnote{\small \url{https://en.wikipedia.org/wiki/Pareto_principle}} that ``states that, for many events, roughly 80\% of the effects come from 20\% of the causes''. The critical thing for data approximation is to determine which part of data is relevant to tasks (belong to the 20\%).
 By this principle, for many big analytic tasks, one may only need to keep a small amount of the data to derive high quality answers.
For example, when we are to build a predictive model on the stock of razers for an online store based on the order history of customers, orders from men are good enough. While on the stock of lipsticks, those from women are good enough. That is to say,  it is not necessary to use the entire data for certain data analytic tasks.

However, it should be pointed out that there are data analytic tasks such that data approximation could not work well. For example, an online store needs to count the total number of goods in its catalog.  Essentially entire goods should be considered for this task, and if a (small) portion of goods are chosen, it is hard to have a ``satisfiable'' result.

We next explain data approximation computation in more detail using three different data analytic tasks.

@@

\begin{figure}[tb!]
  \vspace{-1ex}
  \begin{center}
  \includegraphics[scale=0.5]{./dataApprox.png}
  \end{center}
  \vspace{-3ex}
  \caption{Data approximation}\label{fig-tech-dataappro}
  \vspace{-2ex}
\end{figure}

### 2018-01-26 ApproxComp/sec-introduction.tex

We explain the idea and rational of query approximation,  and show efficiency can be obtained with high effectiveness in practice by its embodiment for graph pattern matching, trajectory compression and dense subgraph computation.

We explain the idea and rational of data approximation,  and show efficiency can be obtained even without sacrificing for effectiveness in practice by its embodiment for shortest paths/distances and link prediction.

>>>>

We explain the idea and rationale of query approximation,  and show efficiency can be obtained with high effectiveness in practice by its embodiment for graph pattern matching, trajectory compression and dense subgraph computation.

We explain the idea and rationale of data approximation,  and show efficiency can be obtained even without sacrificing for effectiveness in practice by its embodiment for shortest paths/distances and link prediction.

### 2018-01-26 ApproxComp/sec-query.tex

Query approximation deals with complex queries involved with big data analytic tasks. Given a class $Q$ of data analytic queries with higher computational complexity,  query approximation is to transform into another class $Q'$ of queries with lower computational complexity and satisfiable approximate answers, as depicted in Fig.~\ref{fig-tech-queryappro} in which $Q$, $Q'$ and $D$ denote the original query, approximate query and data, respectively. Query approximation needs to reach a balance between the query efficiency and answer accuracy when approximating $Q$ with $Q'$.

The rationale behind query approximation has inexact or approximate answers are acceptable for many big data analytic tasks.
On one hand, when the volume of data is extremely large, it may be impossible or not necessary to compute the exact queries.
Observe that nobody would try each and every store to find a pair of shoes with the best cost-performance ratio.
That is, inexact (approximate) solutions are good candidates in this case.
%
On the other hand, when taking noises (common for big data) into account, it may not always a good idea to compute exact answers
for those data analytic tasks whose answers are rare or hard to identify, such as the detection of homegrown violent extremists (HVEs) who seek to commit acts of terrorism in the United States and abroad~\cite{HungJ16}, as exact solutions may have a high chance to miss possible candidates.

We next explain query approximation computation in more detail with three different data analytic tasks.

\begin{figure}[tb!]
  \vspace{-1ex}
  \begin{center}
  \includegraphics[scale=0.45]{./queryApprox.png}
  \end{center}
  \vspace{-3ex}
  \caption{Query approximation}\label{fig-tech-queryappro}
  \vspace{-2ex}
\end{figure}

>>>>

Query approximation deals with complex queries involved with big data analytic tasks. Given a class $Q$ of data analytic queries with high a computational complexity,  query approximation is to transform into another class $Q'$ of queries with a low computational complexity and satisfiable approximate answers, as depicted in Fig.~\ref{fig-tech-queryappro} in which $Q$, $Q'$,  $D$ and $R$ denote the original query, approximate query, data and query result, respectively. Query approximation needs to reach a balance between the query efficiency and answer quality when approximating $Q$ with $Q'$.

The rationale behind query approximation lies in that inexact or approximate answers are sufficient or acceptable for many big data analytic tasks.
On one hand, when the volume of data is extremely large, it may be impossible or not necessary to compute the exact answers.
Observe that nobody would try each and every store to find a pair of shoes with the best cost-performance ratio.
That is, inexact (approximate) solutions are good enough in this case.
%
On the other hand, when taking noises (common for big data) into account, it may not always be a good idea to compute exact answers
for those data analytic tasks whose answers are rare or hard to identify, such as the detection of homegrown violent extremists (HVEs) who seek to commit acts of terrorism in the United States and abroad~\cite{HungJ16}, as exact solutions may have a high chance to miss possible candidates.

We next explain query approximation computation in more detail using three different data analytic tasks.

\begin{figure}[tb!]
  \vspace{-1ex}
  \begin{center}
  \includegraphics[scale=0.5]{./queryApprox.png}
  \end{center}
  \vspace{-3ex}
  \caption{Query approximation}\label{fig-tech-queryappro}
  \vspace{-2ex}
\end{figure}
